Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-02 paper/current/main.tex
added org label table to the manuscript

@@

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to organizations, and a sample of individual states are highlighted.
		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
		The grey box corresponds to the top 20 and bottom 20 ranks.
	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
	}
	\label{fig:semaxis}
\end{figure}

@@

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
		There is no evidence of major changes in publication patterns of mobile authors during this time period.
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased.
		\textbf{c.}
		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time.
		\textbf{d.}
		The proportion of authors publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion.
		However, the proportion of Social Science and Humanities publications has been steadily increasing.
	}
	\label{fig:supp:pubs_over_time}
\end{figure}

@@

%
% Figure - SemAxis By State
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis by U.S. state.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
		Grey points correspond to all other U.S. universities.
	}
	\label{fig:supp:semaxis_states}
\end{figure}

%
% Figure - SemAxis By Sector
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
		Grey points correspond to all U.S. universities.
	}
	\label{fig:supp:semaxis_sectors}
\end{figure}

>>>>

\usepackage{changepage}

@@

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to organizations, and a sample of individual states are highlighted.
		Full organization names listed in Table~\ref{table:supp:orglabels}.
		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
		The grey box corresponds to the top 20 and bottom 20 ranks.
	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
	}
	\label{fig:semaxis}
\end{figure}

@@

% latex table generated in R 3.5.1 by xtable 1.8-2 package
% Thu Apr  2 13:43:00 2020
\begin{table}[ht]
\centering
\caption{\textbf{Full organization names}}
\label{table:supp:orglabels}
\begin{adjustwidth}{-2cm}{}
\begingroup\scriptsize
\begin{tabular}{llll}
  \hline
Short & Full & Short & Full \\ 
  \hline
Stanford & Stanford Univ & Northwestern & Northwestern Univ \\ 
  Columbia & Columbia Univ & Ball State & Ball State Univ \\ 
  Harvard & Harvard Univ & IU Bloomington & Indiana Univ, Bloomington \\ 
  UCLA & Univ of California, Los Angeles & Stevens Institute & Stevens Institute of Technology \\ 
  Cal State Long Beach & California State Univ, Long Beach & NJIT & New Jersey Institute of Technology \\ 
  Wright State & Wright State Univ & NYU & New York Univ \\ 
  U Toledo & Univ of Toledo & SUNY Albany & Univ at Albany, The State Univ of New York \\ 
  Boston U & Boston Univ & NY Medical College & New York Medical College \\ 
  Suffolk & Suffolk Univ & Miami University & Miami Univ \\ 
  CUNY & City Univ of New York (CUNY) & IU Pennsylvania & Indiana Univ of Pennsylvania \\ 
  U Arizona & Univ of Arizona & Baylor & Baylor College of Medicine \\ 
  OSU & Ohio State Univ & UT Health Center & Univ of Texas Health Science Center \\ 
  MIT & Massachusetts Institute of Technology & Bard College & Bard College \\ 
  Princeton & Princeton Univ & Stonehill College & Stonehill College \\ 
  GCU & Grand Canyon Univ & Carleton College & Carleton College \\ 
  Northcentral & Northcentral Univ & Hanover College & Hanover College \\ 
  UCSF & Univ of California, San Francisco & Queens College & Queens College \\ 
  Fielding & Fielding Graduate Univ & DePauw & DePauw College \\ 
  Pepperdine & Pepperdine Univ & Naval Academy & United States Naval Academy \\ 
  Argosy & Argosy Univ & Cal State San Marcos & California State Univeristy San Marcos \\ 
  Yale & Yale Univ & Broad Inst & Broad Institute \\ 
  U Hartford & Univ of Hartford & Forsyth Inst & Forsyth Institute \\ 
  FAU & Florida Atlantic Univ & U Alaska Museum & Univ of Alaska Museum of the North \\ 
  U Miami & Univ of Miami & Lawrence Berkeley & Lawrence Berkeley Natl Laboratory \\ 
  UWF & The Univ of West Florida & Allen Institute & Allen Institute for Brain Science \\ 
  FIT & Florida Institute of Technology & RTI International & RTI InterNatl \\ 
  Purdue & Purdue Univ, West Lafayette & Fermilab & Fermilab \\ 
  Notre Dame & Univ of Notre Dame & State of NY & State of New York \\ 
  Indiana State & Indiana State Univ & Mayo Clinic & Mayo Clinic \\ 
  Saint Mary's & Saint Mary's College & Fish and Wildlife & Fish and Wildlife Research Institute \\ 
  Tufts & Tufts Univ & EPA & United States Emvironmental Protection Agency \\ 
  Mattel & Mattel Children's Hospital & US Army & United States Army \\ 
  Clark & Clark Univ & NSF & Natl Science Foundation \\ 
  UMass Amherst & Univ of Massachusetts Amherst & US Navy & United States Navy \\ 
  Montclair & Montclair State Univ & US Air Force & United States Air Force \\ 
  Farleigh Dickinson & Fairleigh Dickinson Univ-Metro Campus & Ames Laboratory & Ames Laboratory \\ 
  Rockefeller & Rockefeller Univ & Olin College & Oin College of Engineering \\ 
  Adelphi & Adelphi Univ & Scripss Institute & Scripss Institute \\ 
  Barnard & Barnard College & Idaho Natl Lab & Idaho Natl Laboratory \\ 
  Saint John Fisher & Saint John Fisher College & Dana Faber & Dana Faber Cancer Institute \\ 
  U Penn & Univ of Pennsylvania & Dept of Agriculture & United States Department of Agriculture \\ 
  Villanova & Villanova Univ & DOE & United States Department of Energy \\ 
  Widener & Widener Univ-Main Campus & NIAMS & Natl Institute of Arthritis, Skin Diseases \\ 
  Robert Morris & Robert Morris Univ & JMI Labs & JMI Laboratories \\ 
  U Cincinnati & Univ of Cincinnati & Whitehead Inst & Whitehead Institute of Biomedical Research \\ 
  Case Western & Case Western Reserve Univ & Wellesley & Wellesley Univeristy \\ 
  Ashland & Ashland Univ & UT Health, San Antonio & Univ of Texas Health Science Center, San Antonio \\ 
  Texas A\&M & Texas A\&M Univ-Commerce & UNT & Univ of North Texas \\ 
  Texas Southern & Texas Southern Univ & UT Southwestern Med & Univ of Texas Southwestern Medical Center \\ 
  Baylor & Univ of Mary Hardin-Baylor & UT El Paso & Univ of Texas, El Paso \\ 
  U Washington & Univ of Washington - Seattle & USF & Univ of South Florida, Tampa \\ 
  Washington State & Washington State Univ & Florida A\&M & Florida Agricultural and Mechanical Univ \\ 
  Seattle Pacific & Seattle Pacific Univ & Barry & Barry Univ \\ 
  Cal State Fresno & California State Univ-Fresno & UMass Dartmouth & Univ of Massachusetts Dartmouth \\ 
  Northern Arizona & Northern Arizona Univ & Worcester Poly & Worcester Polytechnic Institute \\ 
  IUPUI & Indiana Univ - Purdue Univ Indianapolis & Umass Boston & Univ of Massachusetts Boston \\ 
  U Dayton & Univ of Dayton & MGH Inst & MGH Institute of Health Professions \\ 
  U Conn & Univ of Connecticut & Joseph W. Jones Center & Joseph W. Jones Ecological Research Center \\ 
  ASU & Arizona State Univ & Vaccine Research Center & Vaccine Research Center, San Diego \\ 
  U Florida & Univ of Florida & LA Ag Center & Lousianna Agricultural Center \\ 
  Northern Illinois & Northern Illinois Univ & FL Fish and Wildlife & Florida Fish and Wildlife Conservation Commission \\ 
  Condordia Chicago & Concordia Univ-Chicago & NHLBI & Natl Heart, Lung, and Blood Institute \\ 
  U Chicago & Univ of Chicago & NY Dept. of Health & New York Department of Health \\ 
  SIU Edwardsville & Southern Illinois Univ, Edwardsville & St Michaels & Saint Michaels College \\ 
  SIU Carbondale & Southern Illinois Univ, Carbondale &  &  \\ 
   \hline
\end{tabular}
\endgroup
\end{adjustwidth}
\end{table}

\newpage
%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
		There is no evidence of major changes in publication patterns of mobile authors during this time period.
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased.
		\textbf{c.}
		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time.
		\textbf{d.}
		The proportion of authors publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion.
		However, the proportion of Social Science and Humanities publications has been steadily increasing.
	}
	\label{fig:supp:pubs_over_time}
\end{figure}

@@

%
% Figure - SemAxis By State
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis by U.S. state.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
		Grey points correspond to all other U.S. universities.
		Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:supp:semaxis_states}
\end{figure}

%
% Figure - SemAxis By Sector
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top).
		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
		Grey points correspond to all U.S. universities.
	    	Full organization names listed in Table~\ref{table:supp:orglabels}.
	}
	\label{fig:supp:semaxis_sectors}
\end{figure}
